Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-06-29 manuscripts/manuscript1_supplement.qmd
stuff

@@

  left <- models$"Left Hemisphere Prior" |>
    spread_draws(b_ich_lateralityRight) |>
    mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
    summarize(
      aor = quantile(ich_right_or, 0.5),
      lower_ci = quantile(ich_right_or, 0.025),
      upper_ci = quantile(ich_right_or, 0.975),
      or_1 = sum(ich_right_or > 1) / n(),
      rope = sum(ich_right_or > 1.05 | ich_right_or < 0.95) / n()
    )

@@

  prior_prediction_summary <- left_join(prediction_summary, prior_summary, by = "prior") |>
    gt(rowname_col = "prior") |>
    tab_stubhead(label = "Type of Prior") |>
    fmt_number(columns = everything(), decimals = 2) |>
    fmt_number(columns = 6, rows = 4, decimals = 0) |>
    fmt_percent(columns = 2:3, rows = 1:4, decimals = 1) |>
    tab_header(
      title = md("**Prior Predictive Checks**")
    ) |>
    cols_label(
      Left = "Left Hemisphere",
      Right = "Right Hemisphere",
      aor = "aOR",
      lower_ci = "Lower 95% Credible Interval",
      upper_ci = "Upper 95% Credible Interval",
      or_1 = "Probability of Difference (aOR >1)",
      rope = "% of Distribution outside of ROPE"
    ) |>
    cols_width(
      1 ~ pct(50)
    )

@@

@@

### Neurosurgical Intervention

```{r prior predictive check - neurosurgery}
#| echo: false
#| warning: false

@@

### Ventriculostomy

@@

predictions(neutral_model, by = "ich_laterality") |>
  posterior_draws() |>
  ggplot(aes(x = draw, fill = ich_laterality)) +
  geom_density(alpha = .3) +
  scale_fill_manual(values = c("#422f05", "#E69F00")) +
  scale_x_continuous(labels = scales::percent) +
  labs(
    title = "Predicted Probability",
    fill = "ICH Laterality",
    y = NULL
  )

avg_comparisons(neutral_model, variables = "ich_laterality") |>
  posterior_draws() |>
  ggplot(aes(x = draw)) +
  geom_density(color = "#422f05", fill = "#E69F00") +
  scale_x_continuous(labels = scales::percent) +
  labs(
    title = "Average Difference between Left vs. Right Hemisphere",
    y = NULL
  ) +
  geom_vline(
    xintercept = 0, linetype = "dashed",
    color = "#999999", linewidth = 1
  )

neutral_model |>
  spread_draws(b_ich_lateralityRight) |>
  mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
  ggplot(aes(ich_right_or)) +
  geom_density(color = "#422f05", fill = "#E69F00") +
  # stat_halfeye(aes(fill_ramp = stat(x > 1), fill = "#E69F00", color = "#422f05")) +
  scale_x_continuous(breaks = seq(0, 3, 0.25)) +
  labs(
    title = "Odds Ratio - Right Hemisphere",
    y = NULL,
    fill = NULL
  ) +
  geom_vline(
    xintercept = 1, linetype = "dashed",
    color = "#999999", linewidth = 1
  )

>>>>

### Prior Predictive Checks

@@

  left <- models$"Left Hemisphere Prior" |>
    spread_draws(b_ich_lateralityRight) |>
    mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
    summarize(
      aor = quantile(ich_right_or, 0.5),
      lower_ci = quantile(ich_right_or, 0.025),
      upper_ci = quantile(ich_right_or, 0.975),
      or_1 = sum(ich_right_or < 1) / n(),
      rope = sum(ich_right_or > 1.05 | ich_right_or < 0.95) / n()
    )

@@

  prior_prediction_summary <- left_join(prediction_summary, prior_summary, by = "prior") |>
    gt(rowname_col = "prior") |>
    tab_stubhead(label = "Type of Prior") |>
    fmt_number(columns = everything(), decimals = 2) |>
    fmt_number(columns = 6, rows = 4, decimals = 0) |>
    fmt_percent(columns = 2:3, rows = 1:4, decimals = 1) |>
    tab_header(
      title = md("**Prior Predictive Checks**")
    ) |>
    cols_label(
      Left = "Left Hemisphere",
      Right = "Right Hemisphere",
      aor = "aOR",
      lower_ci = "Lower 95% Credible Interval",
      upper_ci = "Upper 95% Credible Interval",
      or_1 = "Probability of Difference (aOR >1)",
      rope = "% of Distribution outside of ROPE"
    ) |>
    cols_width(
      1 ~ pct(50)
    ) |>
    tab_footnote(
      footnote = "For left hemisphere prior, the p(aOR) < 1 is shown",
      locations = cells_column_labels(columns = 7)
    )

@@

results_visual <- function(model, title) {
  model <- model
  subtitle <- title

  draws <- model |>
    spread_draws(b_ich_lateralityRight) |>
    mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
    summarize()

  pred <- predictions(model, by = "ich_laterality") |>
    tibble()

  theme_ich <- function(base_family = "Inter",
                        base_size = 14) {
    theme_minimal(base_size = base_size) +
      theme(
        text = element_text(lineheight = 2),
        plot.title = element_text(size = rel(1.3), margin = margin(12, 0, 8, 0)),
        plot.subtitle = element_text(size = rel(1.1), margin = margin(4, 0, 0, 0)),
        axis.text.y = element_text(size = rel(0.8)),
        axis.title.y = element_text(size = 12, margin = margin(0, 4, 0, 0)),
        axis.text.x = element_text(size = rel(2)),
        axis.title.x = element_blank(),
        legend.position = "bottom",
        legend.justification = 1,
        panel.grid = element_line(colour = "#F3F4F5"),
        plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
        plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
      )
  }

  p1 <- predictions(model, by = "ich_laterality") |>
    posterior_draws() |>
    ggplot(aes(x = draw, fill = ich_laterality)) +
    geom_density(alpha = .7) +
    scale_fill_manual(values = c("#054224", "#ff8800")) +
    scale_x_continuous(labels = scales::percent) +
    labs(
      title = "Predicted Probability",
      fill = "ICH Laterality",
      y = NULL
    ) +
    theme_ich()

  p2 <- avg_comparisons(model, variables = "ich_laterality") |>
    posterior_draws() |>
    ggplot(aes(x = draw)) +
    geom_density(color = "#054224", fill = "#ff8800") +
    scale_x_continuous(labels = scales::percent) +
    labs(
      title = "Average Difference between Left vs. Right Hemisphere",
      y = NULL
    ) +
    geom_vline(
      xintercept = 0, linetype = "dashed",
      color = "#999999", linewidth = 1
    ) +
    theme_ich()

  p3 <- model |>
    spread_draws(b_ich_lateralityRight) |>
    mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
    ggplot(aes(ich_right_or)) +
    geom_density(color = "#054224", fill = "#ff8800") +
    # stat_halfeye(aes(fill_ramp = stat(x > 1), fill = "#E69F00", color = "#422f05")) +
    scale_x_continuous(breaks = seq(0, 3, 0.25)) +
    labs(
      title = "Odds Ratio - Right Hemisphere",
      y = NULL,
      fill = NULL
    ) +
    geom_vline(
      xintercept = 1, linetype = "dashed",
      color = "#999999", linewidth = 1
    ) +
    theme_ich() +
    theme(legend.position = "none")

  total <- p1 / p2 / p3

  final <- total +
    plot_annotation(
      title = glue(subtitle),
      theme = theme(plot.title = element_text(size = rel(2), margin = margin(12, 0, 8, 0)))
    )

  return(final)
}

@@

#### Neurosurgical Intervention

```{r prior predictive check - neurosurgery}
#| echo: false
#| warning: false
#| fig-height: 12

@@

#### Ventriculostomy

@@

#### Tracheostomy

```{r prior predictive check - tracheostomy}
#| echo: false
#| warning: false

neutral_model <- with_dir(here(), tar_read(m_prior_neutral_tracheostomy))
left_model <- with_dir(here(), tar_read(m_prior_left_tracheostomy))
right_model <- with_dir(here(), tar_read(m_prior_right_tracheostomy))
flat_model <- with_dir(here(), tar_read(m_prior_flat_tracheostomy))

#### Days of Mechanical Ventilation

```{r prior predictive check - vent}
#| echo: false
#| warning: false

neutral_model <- with_dir(here(), tar_read(m_prior_neutral_days_mechanical_ventilation))
left_model <- with_dir(here(), tar_read(m_prior_left_days_mechanical_ventilation))
right_model <- with_dir(here(), tar_read(m_prior_right_days_mechanical_ventilation))
flat_model <- with_dir(here(), tar_read(m_prior_flat_days_mechanical_ventilation))

#### Comfort Care

```{r prior predictive check - comfort}
#| echo: false
#| warning: false

neutral_model <- with_dir(here(), tar_read(m_prior_neutral_comfort))
left_model <- with_dir(here(), tar_read(m_prior_left_comfort))
right_model <- with_dir(here(), tar_read(m_prior_right_comfort))
flat_model <- with_dir(here(), tar_read(m_prior_flat_comfort))

#### Early WLST

```{r prior predictive check - early wlst}
#| echo: false
#| warning: false

neutral_model <- with_dir(here(), tar_read(m_prior_neutral_early_wlst))
left_model <- with_dir(here(), tar_read(m_prior_left_early_wlst))
right_model <- with_dir(here(), tar_read(m_prior_right_early_wlst))
flat_model <- with_dir(here(), tar_read(m_prior_flat_early_wlst))

#### DNR

```{r prior predictive check - dnr}
#| echo: false
#| warning: false

neutral_model <- with_dir(here(), tar_read(m_prior_neutral_dnr_binary))
left_model <- with_dir(here(), tar_read(m_prior_left_dnr_binary))
right_model <- with_dir(here(), tar_read(m_prior_right_dnr_binary))
flat_model <- with_dir(here(), tar_read(m_prior_flat_dnr_binary))
